### 2016-07-08 paper/icse2017/intro.tex
another pass

Optimizing regression testing is important.  As software evolves the
size of test sets (both in number and length of tests) increases,
potentially leading to increasing disruption of the development
process caused by late reports of test failures.  This problem
manifests more dramatically at large IT companies (e.g.,\Comment{
  Groupon~\Fix{cite},} Google~\Fix{cite} and Microsoft~\Fix{cite})
where the size of test sets often exceeds the size of the code base.
Several approaches have been proposed to optimize test execution.
Research has focused mostly on test selection~\Fix{cite}, test
reduction~\Fix{cite}, and test prioritization~\Fix{cite}.  Although
these approaches can also be applied in industrial settings, the focus
in industry has been mostly in parallelizing test execution with
server farms, where worker machines from the farm are assigned to
execute distinct subsets of the original test suite.

Given the proliferation of multicore machines it is not surprising
that popular testing frameworks and build systems provide today
support for parallel test execution~\Fix{cite}.  These solutions
attempt to maximize CPU usage in individual machines with the goal of
running tests more efficiently.  In the case of the Java language, it
is possible to explore parallelism across JVMs and within the JVM.  We
conjecture that such lower-level solutions that use commodity hardware
to optimize test execution are also important (compared to
higher-level parallelism from server farms).  For the scenario of
large IT organizations, lower-level parallelization schemes leverage
the computing power on each individual node of a server farm in
addition to the aggregate processing power of the farm.  Lower-level
parallelization fits particularly well smaller organizations
(/projects) with relatively high testing costs but lower budgets.

>>>>

Optimizing regression testing is important.  As software evolves the
size of test sets increases, potentially leading to disruption of the
development process caused by late reports of test failures.  This
problem manifests more dramatically at large IT companies
(e.g.,\Comment{ Groupon~\Fix{cite},} Google~\Fix{cite} and
Microsoft~\Fix{cite}) where the size of test sets often exceeds the
size of the code base.  Several approaches have been proposed to
optimize regression testing.  Research has focused mostly on test
selection~\Fix{cite}, test reduction~\Fix{cite}, and test
prioritization~\Fix{cite}.  Although these approaches can also be
applied in industrial settings, the focus in industry has been mostly
in parallelizing execution of tests using server farms, where worker
machines from the farm are assigned to execute distinct subsets of the
original test suite.

Given the proliferation of multicore machines it is not surprising
that popular testing frameworks and build systems provide today
support for parallel test execution with the goal of running tests
more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
These solutions use commodity hardware to maximize CPU usage in
individual machines.  In the case of the Java language, it is possible
to explore parallelism across JVMs and within the JVM.  The
lower-level parallelism enabled through build systems is an important
complement to the higher-level parallelism enabled through server
farms.  For the scenario of large IT organizations, lower-level
parallelization schemes leverage the computing power on each
individual node of a server farm in addition to the aggregate
processing power of the farm.  Lower-level parallelism fits
particularly well smaller organizations (/projects) with relatively
high testing costs but lower budgets.
